Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-10 main.tex
vspaces

    \begin{IEEEkeywords}
        DAG, Heterogeneous platform, Adaptive scheduling, Memory constraint.
    \end{IEEEkeywords}

@@

\begin{figure}[tb]
  \centering
  \includegraphics[width=1.0\columnwidth] {images/success-rates-large2}
%  \vspace{-0.8cm}
  \caption{Success rates by workflow size and algorithm on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
%  \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size_barplot}
%    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
%    \vspace{-0.15cm}
\end{figure}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
\new{Due to a varying nature of the workflow generator, some larger workflows can have smaller makespans than their
smaller counterparts due to more parallel execution due to higher fanout or other factors of the workflow's
internal composition.
}

@@

Memory usages on the constrained cluster are depicted in~Fig.~\ref{fig:memory-usage-constrained}.
\new{We plot the average memory usage in the cluster per algorithm and workflow size},
and we observe that the memory footprint of \heftmm remains constant with workflow size.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size-constrained-barplot}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
%    \vspace{-0.15cm}
\end{figure}

@@

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants end with a valid makespan without recomputation.
In case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests.
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is no point in re-scheduling them.
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.
In case of \heftmm, all $290$ workflows can be scheduled initially and all the schedules remain valid until the end.
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.
\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.
\heftbl keeps $105$ schedules valid until the end out of $110$ initial valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}

>>>>

    \begin{IEEEkeywords}
        DAG, Heterogeneous platform, Adaptive \new{workflow} scheduling, Memory constraint.
    \end{IEEEkeywords}

@@

\begin{figure}[tb]
  \centering
  \vspace{-0.4cm}
  \includegraphics[width=1.0\columnwidth] {images/success-rates-large2}
  \caption{Success rates by workflow size and algorithm on the default cluster. Higher is better.}
  \label{fig:success-rates-large}
%  \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
  \vspace{-0.34cm}
  \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size_barplot}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
%    \vspace{-0.15cm}
\end{figure}

@@

Similarly to the default cluster, we observe that the makespan of \heftmm is usually higher
than with \heft (see Fig.~\ref{fig:ms-relations-by-workflow-constrained}), but the \heft schedules are
almost all invalid. It is thus worthwhile to resort to \heftmm for large workflows
in a constrained cluster, since tasks are processed in an order that minimizes
the memory usage of schedule.
\new{Due to a varying nature of the workflow generator, some larger workflows can have smaller makespans than their
smaller counterparts due to more parallelism at nodes with higher out-degree or other factors of the workflow's
internal composition.\todo{TBD: Why here?}}

@@

Memory usage on the constrained cluster are depicted in~Fig.~\ref{fig:memory-usage-constrained}.
\new{We plot the average memory usage in the cluster per algorithm and workflow size},
and we observe that the memory footprint of \heftmm remains constant with workflow size.

@@

\begin{figure}[tb]
    \centering
    \vspace{-0.3cm}
    \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size-constrained-barplot}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
\end{figure}

@@

%\AB{Need to add results on the default cluster!}
%
%    \paragraph{Memory-constrained cluster}
The makespan in case of no recomputation\todo{TBD: clear?} becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160 
for all algorithm variants end with a valid makespan without recomputation.
In case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid until the end, after all the update requests.
The same $13$ experiments end with a valid makespan in case of no recomputation.
So, these workflows require so few resources that there is no point in re-scheduling them.
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.
In case of \heftmm, all $290$ workflows can be scheduled initially and all the schedules remain valid until the end.
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.
\heftblc produces $142$ valid initial schedules and keeps $141$ of them valid until the end.
$50$ experiments are successful without recomputation, a rate of $35\%$ out of all successful final schedules.
\heftbl keeps $105$ schedules valid until the end out of $110$ initial valid schedules.
$55$ remain valid until the end even without recomputation, roughly $50\%$ of all successes.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.95\columnwidth] {images/UpdatesMss2}
    \caption{Relative (excess) makespan of \heftbl, \heftblc and \heftmm\ \new{in case of no recomputation}. Smaller is better.}
    \label{fig:updates-ms}
%    \vspace{-0.3cm}
\end{figure}
